---
title: "Project2_Employees"
output: word_document
---

```{r library}

#library("lubridate") #for date format correction
library("caTools") #split the data into test and train
library("car")
library("corrplot")
library("MASS")
library(nortest) 
#library("mice") #missing data - outliers correction
#library("caret")
#library("lattice")


```
Firstly download the data and split into 70% tranning and 30% test 
```{r setup, include=FALSE}
HR = read.csv("HR_comma_sep.csv", sep=",",dec=".")
head(HR)
summary(HR)


set.seed(1)

HR["spl"] <- NA
HR$spl <- sample.split(HR$spl,SplitRatio=0.7)

HR.train=subset(HR[,-11], HR$spl==TRUE) # where spl== TRUE means to add only those rows that have value true for spl in the training dataframe
HR.test <- subset(HR[,-11], HR$spl==FALSE)


```

Correlation Analyses
```{r}
#scatterplotMatrix(data_house)
cor_HR <- cor(HR[,c("satisfaction_level","last_evaluation","number_project","average_montly_hours","time_spend_company","Work_accident","promotion_last_5years")])#excluding qualitative and binary variable to correlation plot
corrplot(cor_HR, method="pie")
```
Construction of a model with all variable, as there is no high correlation between them
```{r cars}
mod1 <- glm(left ~ ., family = binomial(link = "logit"), data = HR.train)
?glm
summary(mod1)
```
The variable sales do not contributes to the model, except for sales RandD
Let´s use StepAIC to help the selection of the best model and then compare it with the previous one
```{r}
library("bestglm")

modBIC <- stepAIC(mod1, trace = 0, k = log(nrow(HR.train)))

r2glm <- function(model) {

  summaryLog <- summary(model)
  1 - summaryLog$deviance / summaryLog$null.deviance

}

summary(modBIC)
summary(mod1)

r2glm(modBIC) 
r2glm(mod1)

```
Assumptions:

```{r}
par(mfrow = c(2, 2))
plot(modBIC, c(1,2)) #1-Linearity; 2-Normality;
plot(modBIC$residuals, type = "o") #4-Independence of the errors

```
Formal test to verify normality
```{r}
lillie.test(modBIC$residuals)
```

```{r}
par(mfrow = c(3, 3))
termplot(modBIC, partial.resid = TRUE)

```
Multicolinearity
```{r}
vif(modBIC)
```
Model Accuracy
```{r}
library(caret)
# make predictions
predictions<- predict(modBIC,HR.test, type = "response" )

gmlmodelbinded <- cbind(HR.test,predictions)

gmlmodelbinded$predictions[gmlmodelbinded$predictions < 0.5] <- 0
gmlmodelbinded$predictions[gmlmodelbinded$predictions >= 0.5] <- 1 

summary(gmlmodelbinded)
# summarize results
confMat<- confusionMatrix(gmlmodelbinded$predictions,gmlmodelbinded$left)
confMat

```